Cannibalism among the supermassive black holes

### 2019-03-09 paper.tex
Updates from Overleaf

\subsection{Mergers, Ejections and Kicks}

@@

>>>>

\subsection{Mergers, Ejections and Kicks}
Figure \ref{fig:meosmbh} shows the distribution of merged, ejected and orbiting black holes across all galaxy simulations as a function of guest black hole mass.

@@

\begin{figure}[ht]
\begin{center}
\includegraphics[width=0.45\textwidth]{plots/q_merger_fraction.png}
\caption{Fraction of mergers per BH mass ratio.  Each point represents the fraction of galaxy mergers that led to BH mergers for each BH merger ratio bin.  Note that a "bin" at each point is comprised of the mass ratio at that point up to, but not including, the next point on the x-axis.}
\label{fig:q_merge_fraction}
\end{center}
\end{figure}
